Evaluating the Decency and Consistency of Data Validation Tests Generated by LLMs

### 2023-10-01 paper/paper.qmd
comma to semi-colon fix

Our work additionally contributes to the growing body of work using LLMs to automate portions of the data science workflow. LLMs have already been integrated into software tools such as GitHub's Co-Pilot [@githubcopilot] and AutoGPT [@autogpt] and IDEs such as IntelliJ [@krochmalski2014] and VSCode [@vscode] to produce code in a variety of languages. These tools are and will continue to assist data scientists to accelerate, resolve bugs in, document, and optimize their code in all parts of the data science workflow. LLMs have also demonstrated potential to automate other onerous or tedious tasks in data science pipelines. These include generating synthetic text data [@chung2023; @yu2023], improving search-based software testing [@lemieux2023], generating unit tests from natural language in a variety of programming languages and contexts [@lahiri2022, @schafer2023], generating property-based tests from API documentation [@vikram2023large], and conducting exploratory data analysis [@ma2023]. As LLM prompting and fine-tuning methods improve, they will reduce technical barriers to conducting transparent, accurate, reproducible analysis, enabling data scientists to be more productive and put their energy towards analysis. higher-order reasoning, and sophisticated inference. The work described in this paper towards automating data validation using LLMs has the capacity to further this evolution.

@@

A limitation of our work on prompt engineering (and indeed of prompt engineering generally) is that we are unable to provide fully reliable explanations for improvements in performance. Though we can make convincing speculations, these are ultimately educated guesses. Previous studies have shown that in addition to being brittle to precise semantics [@arora2022, @zhao2021], prompts show improved performance from additional text which provides no new information [@henrickson2023] such as naming the model (e.g., “You are Frederick, a helpful AI”), emulating the chatbot saying that it understands the instructions, asking it to output the “right conclusion”, and providing positive feedback [@clavie2023]. Despite the opacity of the emergent properties of LLMs, we may be able to develop greater understanding of the impacts of prompting choices by testing these prompts on a greater diversity of datasets from across disciplines and contexts.

>>>>

Our work additionally contributes to the growing body of work using LLMs to automate portions of the data science workflow. LLMs have already been integrated into software tools such as GitHub's Co-Pilot [@githubcopilot] and AutoGPT [@autogpt] and IDEs such as IntelliJ [@krochmalski2014] and VSCode [@vscode] to produce code in a variety of languages. These tools are and will continue to assist data scientists to accelerate, resolve bugs in, document, and optimize their code in all parts of the data science workflow. LLMs have also demonstrated potential to automate other onerous or tedious tasks in data science pipelines. These include generating synthetic text data [@chung2023; @yu2023], improving search-based software testing [@lemieux2023], generating unit tests from natural language in a variety of programming languages and contexts [@lahiri2022; @schafer2023], generating property-based tests from API documentation [@vikram2023large], and conducting exploratory data analysis [@ma2023]. As LLM prompting and fine-tuning methods improve, they will reduce technical barriers to conducting transparent, accurate, reproducible analysis, enabling data scientists to be more productive and put their energy towards analysis. higher-order reasoning, and sophisticated inference. The work described in this paper towards automating data validation using LLMs has the capacity to further this evolution.

@@

A limitation of our work on prompt engineering (and indeed of prompt engineering generally) is that we are unable to provide fully reliable explanations for improvements in performance. Though we can make convincing speculations, these are ultimately educated guesses. Previous studies have shown that in addition to being brittle to precise semantics [@arora2022; @zhao2021], prompts show improved performance from additional text which provides no new information [@henrickson2023] such as naming the model (e.g., “You are Frederick, a helpful AI”), emulating the chatbot saying that it understands the instructions, asking it to output the “right conclusion”, and providing positive feedback [@clavie2023]. Despite the opacity of the emergent properties of LLMs, we may be able to develop greater understanding of the impacts of prompting choices by testing these prompts on a greater diversity of datasets from across disciplines and contexts.
